Coding Strategies in Baker's Game

### 2021-05-10 articles/bakers-game-coding/article.tex
add toy result on baker's game

\title{Dual selection games}

@@

\begin{abstract}
  Often, a given selection game studied in the literature has
  a known dual game. In dual games, a winning
  strategy for a player in either game may be used to create
  a winning strategy for the opponent in the dual. 
  For example, the Rothberger selection game involving open covers
  is dual to the point-open game. This extends to a general
  theorem: if \(\{\ran{f}:f\in\mathbf C(\mc R)\}\) is coinitial in \(\mc A\)
  with respect to \(\subseteq\),
  where \(\mathbf C(\mc R)=\{f\in(\bigcup\mc R)^{\mc R}:R\in\mc R\Rightarrow f(R)\in R\}\) 
  collects the choice functions on the set \(\mc R\),
  then \(G_1(\mc A,\mc B)\) and \(G_1(\mc R,\neg\mc B)\)
  are dual selection games. 
\end{abstract}

@@

\section{Introduction}

@@

>>>>

\title{Coding Strategies in Baker's Game}

@@

\begin{abstract}
TODO
\end{abstract}

@@

\begin{abstract}
TODO
\end{abstract}

Let \(f^\leftarrow(y)=\setB{x\in A}{f(x)=y}\).

\begin{proposition}\label{denseThreads}
There exists a function \(f:\mathbb R\to\mathbb R^{<\omega}\) such that
for each \(s\in\mathbb R^{<\omega}\), \(f^\leftarrow(s)\) is dense in \(\mathbb R\).
\end{proposition}

\begin{proof}
Noting that \(|\mathbb R^{<\omega}|=|\mathbb R|=\mathfrak c\), we recall that
\(\mathbb R\) may be partitioned into \(\mathfrak c\)-many parts, each dense in
\(\mathbb R\) (e.g., the equivalence classes of \(x\sim y\) iff \(x-y\in\mathbb Q\)).
We may then let \(f\) assign each equivalence class to a distinct sequence in
\(\mathbb R^{<\omega}\).
\end{proof}

(We thank Lynne Yengulalp for
suggesting the partition result that greatly simplified the preceding proof.)

\begin{theorem}
\(\plII\win G(W)\) if and only if \(\plII\codewin G(W)\).
\end{theorem}
\begin{proof}
We need only show 
\(\plII\notcodewin G(W)\) implies \(\plII\notwin G(W)\).
Let \(\sigma\) be a perfect-information strategy for \(\plII\),
and let \(f\) be given by Prop \ref{denseThreads}.

First, we choose
\[
\tau(\tuple{a_0})\in
\big(a_0,\sigma(\tuple{a_0})\big)\cap
f^\leftarrow\big(\tuple{a_0}\big)
\]
that is, we guarantee \(a_0<\tau(\tuple{a_0})<\sigma(\tuple{a_0})\)
and \(f\big(\tau(\tuple{a_0})\big)=\tuple{a_0}\).

Given \(b_n,a_{n+1}\), define
\(b_n'=\min\big(b_n,\sigma(f(b_n)\concat\tuple{a_{n+1}})\big)\),
noting \(a_{n+1}<b_n'\). Now choose
\[
\tau(\tuple{b_n,a_{n+1}})\in
\big(a_{n+1},b'\big)\cap
f^\leftarrow\big(f(b_n)\concat\tuple{a_{n+1}}\big)
\]
that is, we guarantee
\(a_{n+1}<\tau(\tuple{b_n,a_{n+1}})<b_n'\leq b_n\) and
\(f\big(\tau(\tuple{b_n,a_{n+1}})\big)=f(b_n)\concat\tuple{a_{n+1}}\).

Then \(\tau\) defines a coding strategy for \(\plII\); suppose it is
defeated by \(\plI\) choosing \(a_n\) during round \(n\).

Then if \(b_n\) is the move designated by \(\tau\) for player \(\plII\)
during round \(n\), that is, \(b_0=\tau(\tuple{a_0})\) and
\(b_{n+1}=\tau(\tuple{b_n,a_{n+1}})\),
we have \(f(b_n)=\tuple{a_0,\dots,a_n}\).

First, we see that
\[a_0<a_1<\tau(\tuple{a_0})<\sigma(\tuple{a_0})\]

And finally, we see that
\[a_{n+1}<a_{n+2}<\tau(\tuple{b_n,a_{n+1}})<b_n'\leq
\sigma(f(b_n)\concat\tuple{a_{n+1}})=\sigma(\tuple{a_0,\dots,a_{n+1}})\]

Therefore we have shown that \(a_n\) is also a legal move against the
perfect information strategy \(\sigma\) each round, and therefore
\(\sigma\) is also not a winning strategy.
\end{proof}

\section{TODO}

In such a game \(G\), players \(\plI\)\end{proof}

\section{TODO}

@@

Often when defining games, \(\plI\) and \(\plII\) alternate making choices
\(a_n\in M\) and \(b_n\in M\) during each round \(n<\omega\), 
and \(\plII\) wins the game if and only if \(\<a_0,b_0,a_1,b_1,\dots\>\in W\).
